New insights into the Weddell Sea ecosystem applying a quantitative network approach

### 2022-12-29 Manuscript/Manuscript.tex
Updated biblio

\begin{abstract}
Network approaches can shed light on the structure and stability of
complex marine communities. In recent years, such approaches have been
successfully applied to study polar ecosystems, improving our knowledge
on how they might respond to ongoing environmental changes. The Weddell
Sea is one of the most studied marine ecosystems outside the Antarctic
Peninsula in the Southern Ocean. Yet, few studies consider the known
complexity of the Weddell Sea food web which in its current form
comprises 490 species and 16041 predator-prey interactions. Here we
analysed the Weddell Sea food web, focusing on trophic interactions that
underpin ecosystem structure and stability. We estimated the strength
for each interaction in the food web, characterised species position in
the food web using unweighted and weighted properties, and analysed
species' roles with respect to the stability of the food web. On one
hand, we found that the distribution of the interaction strength at the
food web level is asymmetric, where weak interactions are prevalent.
Including such information as a (weighted) property for species we
detected a positive relationship between species mean interaction
strength and two unweighted properties, trophic level and the total
number of interactions. We also found that only a few species are key in
terms of food web stability, presenting high mean interaction strength,
mid to high trophic level, relatively high number of interactions, and
mid to low trophic similarity. In the same analysis we have integrated
food web and species information, enabling a more complete assessment of
the ecosystem structure and function, likely highlighting the ecological
processes at play in the Weddell Sea. We consider that our results
provide new insights important for the development of effective policies
and management strategies, particularly given the ongoing initiative to
implement a Marine Protected Area (MPA) in the Weddell Sea.
\end{abstract}

@@

Food web analysis constitutes an important framework for understanding
ecological community structure and for conserving biodiversity through
ecosystem management \citep{Thompson2012}. Although topological food web
analysis, which considers only the presence and absence of predator-prey
interactions, provides important insights into the structure and
functioning of ecological communities
\citep[e.g.][]{Pascual2006, Kortsch2015, Marina2018, Cordone2020, Rodriguez2022},
more information on the nature of the trophic interactions is needed to
effectively charaterise ecosystem dynamics and stability
\citep[\citet{otherRefs}]{Kortsch2021}. This is a fundamental step for
providing assemessments on ecosystem vulnerability to environmental
pressures and for prioritising management actions. In this regard,
quantifying the strength of trohic interactions and species' roles
within the network are of paramount importance
\citep{Carrara2015, Allesina2015, Nilsson2016, Cirtwill2018a}.

We should maybe write a paragraph about weighted and unweighted
approaches here, where we aslo introduce the approach we used\ldots{}

\begin{quote}
{[}susanne{]} I moved the paragraph below. it makes more sense to first
talk about polar regions in genaral and then introduce the Weddell Sea.

Using a network approach, different types (e.g., terrestial, lake, etc.)
of food webs from various geographic locations are studied worldwide,
including marine polar food webs
\citep{Carscallen2012, Santana2013, Kortsch2019, Pecuchet2022}. Some of
these studies from the Arctic show how food web properties (e.g.,
connectance) are constrained by environmental factors such as sea ice
cover and seawater temperature \citep{Kortsch2019, Pecuchet2022}. In the
Southern Ocean, important insights have been gained into mechanisms of
energy flow, the relative importance and traits of individual species
and the influence of environmental variables (e.g., sea-ice) on the
structure of local food webs \citep{Cordone2020, Rossi2019}.
{[}susanne{]} what do you mean here: the relative importance and traits
of individual species? What important mechanisms? Can we be more
specefic? Can we also be more specific about how environmental variables
(e.g., sea-ice) influence the structure of local food webs in the SO?
\end{quote}

The Weddell Sea is expected to be one of the last regions of the
Southern Ocean to experience the consequences of climate change due to
its extensive ice cover and ocean currents \citep{Teschke2021} resulting
in less sea surface warming compared to other areas of the Southern
Ocean. Because of these environmental characteristics, the Weddell Sea
may serve as a refuge for Antarctic species which depend on sea ice
(e.g.~krill, emperor penguin, Weddell seal) or have low heat tolerance
(e.g., most notothenioid fishes) due to their adaptations to freezing
tempeartures \citep{Griffiths2017}. While essential large-scale
hydrodynamic relationships are relatively well-known for this region
\citep{deSteur2019}, information on the current distribution, abundance
and sensitivity to climate change is only partially known for a few
species (e.g., XXXXX) \citep{Houstin2022}. \textgreater{}
{[}susanne{]}it is not clear from the text why Weddell Sea is one of the
last regions of the SO to face the consequences of warming, be explicit
here, how are the currents affecting the Weddell Sea? \textgreater{}

Overall, the complexity the Weddell Sea food web is high and consists of
488 species and 16200 predator-prey interactions\citep{Jacob2011}. In an
attempt to better understand species role related to food web stability,
Jacob et al.~(2011) performed secondary extinction experiments and found
that the removal of small to medium-sized, and not large, organisms
caused a cascade of secondary extinctions. This findings highlighted the
relative importance of predators, rather than prey, in the architecture,
functioning and stability of the Weddell Sea food web, which coincides
with findings from recent meta-analyses in natural complex food webs
\citep{Brose2019, Perkins2022}. Other investigations have considered
this food web though in a meta-analysis context\ldots.{[}more text here,
WHAT DO THESE META\_ANALSYES STUDIES SHOW{]}
\citep{Brose2019, Perkins2022, Saravia2022}.

Several methodologies have been applied to estimate the interaction
strength in food webs, where the quantity and quality of data mostly
determine which approach is more convenient \citep{Berlow2004}.
Experimental methods combined with dynamic modelling
\citep{Emmerson2004, Carrara2015}, measurements of species abundances
trough time \citep{Fahimipour2014, Chang2021}, and/or estimation of
metabolic rates and biomass of all species in the community
\citep{Neutel2014}; all these methods require a large experimental
and/or sampling effort that restrict them to simple networks (circa 10
species). Other methods based on predator-prey body mass allometric
relationships \citep{Berlow2009, Pawar2012} could be applied to larger
networks due to less data requirements, although they might have less
power with increasingly complex networks unless more traits are included
in the estimations \citep{Jonsson2018}. For food webs composed by nearly
1000 species and about 20000 interactions only those methods with less
data requirements are feasible. On of these is the one proposed by
\citet{Pawar2012}, which allows to obtain interaction strength
estimations by combining data on body mass (of consumer -predator- and
resource -prey-) and interaction dimensionality (classified as 2 or 3
dimensions).

In this study, we aim to go beyond a purely topological
(presence/absence) assessment of who eats whom in the Weddell Sea
ecosystem by providing a quantitative analysis of the trophic
interaction network. We aim to analyse role for the structure and
stability of the food web. To achieve this, we: 1) estimated the
strength for each interaction in the Weddell Sea food web, 2)
characterised species role considering both weighted and unweighted
properties, and 3) analysed the species' role realted to the stability
of the food web. This is the first time that the interaction strength
was estimated for all the interactions mostly at the species level for
the Weddell sea food web

@@

The high Antarctic Weddell Sea shelf is situated between 74 and 78ºS,
stretching approximately 450 km in length from East to West (Figure 1).
Water depth varies between 200 and 500 meters, and shallower areas are
covered by continental ice, which forms the coastline along the eastern
and southern part of the Weddell Sea. The shelf area contains a complex
three-dimensional benthic habitat with large benthic biomasses,
intermediate to high diversity in comparison to benthic boreal
communities and a spatially patchy distribution of organisms
\citep{Dayton1990, Teixido2002}.

@@

Furthermore, we took a species' habitat into account, which describes
the physical position of a species within the ecosystem. Species were
categorised as: 1) benthic, if a species lives on the seafloor; 2)
pelagic, if a species lives close to the surface; 3) benthopelagic, if
it moves between and connects the mentioned environments; 4) demersal,
if it lives and feeds on or near the bottom of the sea; and 5)
land-based, if the consumer is not strictly aquatic but feeds
predominantly on marine species. Species habitat affiliation was
retrieved from \citet{Jacob2011}.

With the aim of studying the relationship between the interaction
strength of the species (weighted property) and its unweighted
properties we performed linear regression analyses between the log mean
interaction strength and each of the mentioned unweighted properties.
Thus we considered the interaction strength as the dependent variable
and the given unweighted property as the independent variable, and
obtained the coefficients (slope and intercept) for the linear model.
Models were fitted using the least squares approach. We also explored
the mean interaction strength distribution with the species habitat.

@@

To analyse the impact of species on food web stability, we performed
extinction simulations deleting one species at a time, that is for every
extinction network size was reduced by one species only. After each
extinction, we calculated the stability of the network minus the
targeted species (489 nodes) and compared it with that of the whole
network (490 nodes in total). To calculate stability, we used the mean
of the real part of the maximum eigenvalue of the Jacobian matrix using
randomized Jacobians and keeping the predator-prey sign structure fixed
\citep{Allesina2008, Grilli2016}. This index indicates a more stable
food web when it is negative. We performed 1000 simulations for each
species extinction and obtained a mean maximum eigenvalue for each case.
At last we statistically analysed such a difference with an
Anderson-Darling test considering a p-value \textless{} 0.01
\citep{Scholz1987}. If this difference is positive, then the stability
of the food web is higher if a species was removed, and vice versa. A
detailed description on the stability calculations can be found in
Supplementary Material.

Once we had the results for the impact on stability for each species
extinction, we plotted them considering weighted (interaction strength)
and unweighted properties, and species habitat. With this we aim to
characterise those species with a relatively high effect on the
stability of the food web.

@@

Our analyses show that the distribution of species interaction strength
at the network level is asymmetric, i.e., the Weddell Sea food web
contains many weak interactions and only a few strong ones. This finding
is consistent with many previous theoretical and empirical studies
\citep[e.g.][]{McCann1998, Neutel2002, Emmerson2004, Wootton2005, Kortsch2021}.
The asymmetric distribution of interaction strength in food webs has
been interpreted as an explanation for the persistence of complex
communities in nature \citep{Bascompte2005, Allesina2015, Nilsson2016}.
Here we show that this pattern is also prevalent in the Weddell Sea, one
of the most complex food webs to date, comprising 490 species and 16041
predator-prey interactions. This finding is in someway validating the
method we used, validation of allometric methods of IS estimation not
including interaction dimensionality has been performed for microcosmos
of relatively few species \citep{Jonsson2018}.

@@

We employed a range of descriptors using both unweighted and weighted
food web properties to characterise the dynamic and multifaceted nature
of the Weddell Sea food web. Our results show a positive relationship
between interaction strength and trophic level, and between interaction
strength and species degree. Mean interaction strength increases with
trophic level and species degree. The former relationship contradicts
studies that suggest that mid-trophic level species (which, krill???
examples are always good) are involved in the major pathways of energy
flow in high-latitude marine ecosystems
\citep{Pinkerton2014, Murphy2016, McCormack2020, Riccialdelli2020}.
However, this finding could also be explained by the lack of species
biomass information in the calculation of interaction strength using the
methodology we applied \citep{Parwar2012}. The methodlogy by Parwar et
al.(2012) allows information on species density/biomass to be included,
but this type of data was not available for the majority of species in
our food web. In the Weddell Sea, species with high degree also tend to
have high mean interaction strengthsThe positive relationship between
interaction strength and species degree reinforces the central role of
species with many interactions: species with a high degree (hubs) have a
large impact on overall food web structure and functioning
\citep{Dunne2002a, Kortsch2015}. This information on the quantity and
quality of interactions and its relationship enables a robust assessment
of the species' role in the stability of the food web
\citep{Cirtwill2018a}.

@@

Only a few species play a key role with respect to the Weddell Sea food
web stability, according to the mean maximum eigenvalue stability index
employed in this study. This is in concordance with other studies on
complex empirical food webs in marine ecosystems in the Arctic and other
locations in Antarctica \citep{Kortsch2015, Marina2018, Rodriguez2022}.
These key species are characterised by a particular set of food web
properties: high to mean IS; mid to high trophic level; a relatively
high number of interactions; and mid to low trophic similarity. In a
previous study on sequential extinction simulations for the Weddell Sea
food web \citep[!!]{CITA}, it was found that larger bodied-sized species
could be lost without causing a collapse of the network. A major caveat
of this finding, also recognised by the authors, was that population
dynamics were ignored and hence no top-down extinctions, or other
indirect effects, could occur. In our study we considered such top-down
effects by including information on the species IS, which is of
paramount importance when analysing the response of perturbations in
ecological communities \citep{McCann1998, Montoya2009, Novak2011}. Thus,
our study suggests that species with high mean IS and high trophic
levels need to be considered with particular attention when trying to
predict the effects of perturbations on the Weddell Sea ecosystem. This
conclusion is further reinforced by the finding that these species have
mid to low trophic similarity, which means that few other species of the
food web can occupy the same trophic role. In a review, it was
emphasised that polar pelagic communities are particularly sensitive to
changes due to a low functional redundancy at key trophic levels
\citep{Murphy2016}. Here we provide broader analyses of species impact
on food web robustness by including species from all habitats (benthic,
pelagic and land-based). This suggests that the sensitivity of marine
polar ecosystems to environmental perturbations is a concern also beyond
the pelagic realm.

@@

Our study goes beyond the current understanding of how species influence
ecosystem structure and stability in the Weddell Sea in particular and
in most polar regions in general \citep{Murphy2016, McCormack2021}. In
the same analysis we have integrated information about weighted
(interaction strength) and unweighted species properties, enabling a
more complete assessment of the species' role in the food web structure
and function.

We consider that the information provided in this study is important for
the development of effective policies and management strategies,
particularly given the ongoing initiative to implement a Marine
Protected Area (MPA) in the Weddell Sea \citep{Teschke2021}.

@@

\begin{figure}
\includegraphics[width=12cm]{Fig.2_ToyFoodWeb} \caption{Scheme of a network showing the weighted and unweighted properties we used to characterize the species of the Weddell Sea food web.}\label{fig:unnamed-chunk-2}
\end{figure}

>>>>

\begin{abstract}
Network approaches can shed light on the structure and stability of
complex marine communities. In recent years, such approaches have been
successfully applied to study polar ecosystems, improving our knowledge
on how they might respond to ongoing environmental changes. The Weddell
Sea is one of the most studied marine ecosystems outside the Antarctic
Peninsula in the Southern Ocean. Yet, few studies consider the known
complexity of the Weddell Sea food web, which in its current form
comprises 490 species and 16041 predator-prey interactions. Here we
analysed the Weddell Sea food web, focusing on the species and trophic
interactions that underpin ecosystem structure and stability. We
estimated the strength for each interaction in the food web,
characterised species position in the food web using unweighted and
weighted food web properties, and analysed species' roles with respect
to the stability of the food web. We found that the distribution of the
interaction strength at the food web level is asymmetric, with many weak
interactions and few strong ones. We detected a positive relationship
between species mean interaction strength and two unweighted properties
(i.e., trophic level and the total number of interactions). We also
found that only a few species possess key positions in terms of food web
stability. These species are characterised by high mean interaction
strength, mid to high trophic level, relatively high number of
interactions, and mid to low trophic similarity. In this study, we
integrated unweighted and weighted food web information, enabling a more
complete assessment of the ecosystem structure and function of the
Weddell Sea food web. Our results provide new insights, which are
important for the development of effective policies and management
strategies, particularly given the ongoing initiative to implement a
Marine Protected Area (MPA) in the Weddell Sea.
\end{abstract}

@@

Food web analysis constitutes an important framework for understanding
ecological community structure and for conserving biodiversity through
ecosystem management \citep{Thompson2012}. Although topological food web
analysis, which considers only the presence and absence of predator-prey
interactions, provides important insights into the structure and
functioning of ecological communities
\citep[e.g.][]{Pascual2006, Kortsch2015, Marina2018, Cordone2020, Rodriguez2022},
more information on the nature of the trophic interactions is needed to
effectively charaterise ecosystem dynamics and stability
\citep{Kortsch2021}. This is a fundamental step for providing
assemessments on ecosystem vulnerability to environmental pressures and
for prioritising management actions. In this regard, quantifying the
strength of trohic interactions and species' roles within the network
are of paramount importance
\citep{Carrara2015, Allesina2015, Nilsson2016, Cirtwill2018a}.

Estimating interaction strength in food webs allows differentiating the
importance of species interactions. On the contrary, unweighetd food web
representations give equal importantance to all interactions
well-knowing that some species interactions are stronger than others and
hence play a diffrent role for ecosystem functioning and stability. Both
empirical and theoretical studies show that interactions strength
distributions in food webs are assymetric
\citep{Paine1992, McCann1998, Emmerson2004, Wootton2005, Kortsch2021},
containing a few strong and many weak interactions. This asymmetric
patterning of weak and strong links is crucial to food web stability
\citep{Paine1992, McCann1998, Neutel2002}. In a recent paper on an
aquatic food web it was further highlighted that temporal changes in
ecosytem functioning could only be predicted using weighted food web
structure \citep{Kortsch2021}. Hence, in order to assess the stability
and functioning of a food web, it is important to first determine the
quantitative structure of the trophic network.

Several methodologies have been applied to estimate interaction strength
in food webs, where the quantity and quality of the data mostly
determines which approach is the most convenient \citep{Berlow2004}.
Approaches include experimental methods combined with dynamic modelling
\citep{Emmerson2004, Carrara2015}, measurements of species abundances
through time \citep{Fahimipour2014, Chang2021}, and estimation of
metabolic rates and biomass of all species in the community
\citep{Neutel2014}. However, these types of methods require large
experimental set-ups and parameterisations restricting the analyses to
smaller networks (e.g., approximatley 10 species or less). Other methods
based on allometric scaling relationships and biomass information
\citep{Kortsch2021, Gauzens2019} can be applied to larger networks with
less data requirements, but this comes at the expense of precision in
the predictions. For even larger food webs composed of nearly 1000
species and more than 10000 interactions, only methods with even less
data requirements are feasible. One of these methods, proposed by
\citet{Pawar2012}, combines data on consumer and resource body masses
and consumer search space (interaction dimensionality) to obtain
interaction strength estimates for each pairwise predator-prey
interaction. An advantage of this method is that it can be applied
without information on species biomass.

Using a a network approach, different types (e.g., terrestial, lake,
marine) of food webs from various geographic locations are studied
worldwide, including marine polar food webs
\citep{Carscallen2012, Santana2013, Kortsch2019, Pecuchet2022}. Some of
the studies from the Arctic show how food web properties (e.g.,
connectance) are constrained by environmental factors such as sea ice
cover and seawater temperature \citep{Kortsch2019, Pecuchet2022}. In the
Southern Ocean, important insights have been gained into mechanisms of
energy flow, the relative importance of individual species and their
traits, and the influence of environmental variables (e.g., sea-ice) on
the structure of local food webs \citep{Cordone2020, Rossi2019}. For
instance, in Potter Cove (West Antarctic Peninsula) the substratum type
(i.e.~hard/soft or rocks/sediments) plays a significant role in the
structure and stability of the food web. In Terra Nova Bay (Ross Sea),
the architecture of biodiversity was reshaped by the pulsed input of
sympagic food sources following sea-ice break up, with food web
simplification, decreased intraguild predation, potential disturbance
propagation and increased vulnerability to biodiversity loss
\citep{Rossi2019}.

The Weddell Sea is expected to be one of the last regions of the
Southern Ocean to experience the consequences of climate change due to
its extensive ice cover and ocean currents \citep{Teschke2021} resulting
in less sea surface warming compared to other areas of the Southern
Ocean. This Sea plays an important role in driving global thermohaline
circulation and ventilating the global abyssal ocean because it
generates a considerable part of the Antarctic Bottom Water
\citep{Fahrbach2009}. Because of these environmental characteristics,
the Weddell Sea may serve as a refuge for Antarctic species which depend
on sea ice (e.g.~krill, emperor penguin, Weddell seal) or have low heat
tolerance (e.g., most notothenioid fishes) due to their adaptations to
freezing tempeartures \citep{Griffiths2017}. While essential large-scale
hydrodynamic relationships are relatively well-known for this region
\citep{deSteur2019}, information on the current distribution, abundance
and sensitivity to climate change is only partially known for a few
species (e.g., emperor penguin) \citep{Houstin2022}.

The network complexity of the Weddell Sea food web is high comprising
488 species and 16200 predator-prey interactions \citep{Jacob2011}. In
an attempt to better understand species roles related to food web
stability, Jacob et al.~(2011) performed secondary extinction
experiments and found that the removal of small to medium-sized, and not
large, organisms caused a cascade of secondary extinctions. This
findings highlighted the relative importance of predators, rather than
prey, for the architecture, functioning and stability of the Weddell Sea
food web, which coincides with findings from recent meta-analyses in
natural complex food webs \citep{Brose2019, Perkins2022}. Other
investigations considered this food web in a meta-analysis context
showing that high predator-prey body-mass ratios are found for predator
groups with specific trait combinations, including small vertebrates and
large swimming or flying predators \citep{Brose2019}. These trait
combinations generate weak interactions that stabilize communities
against perturbations maintaining ecosystem functioning.

In this study, we aim to go beyond a purely topological
(presence/absence) assessment of who eats whom in the Weddell Sea
ecosystem by providing a quantitative analysis of the trophic
interaction network. We aim to analyse the species' role for the
structure and stability of the food web. To achieve this, we: 1)
estimated the strength for each interaction in the Weddell Sea food web,
2) characterised species' role considering both weighted and unweighted
properties, and 3) analysed the species' role related to the stability
of the food web. This is the first time that interaction strengths were
estimated for all pairwise trophic interactions at the species level
(except for a few) for the Weddell sea food web.

@@

The high Antarctic Weddell Sea shelf is situated between 74 and 78ºS,
stretching approximately 450 km from East to West (Figure 1). Water
depth varies between 200 and 500 meters, and shallower areas are covered
by continental ice, which forms the coastline along the eastern and
southern part of the Weddell Sea. The shelf area contains a complex
three-dimensional benthic habitat with large benthic biomasses,
intermediate to high diversity in comparison to benthic boreal
communities and a spatially patchy distribution of organisms
\citep{Dayton1990, Teixido2002}.

@@

Furthermore, we took species habitat affiliation into account, which
describes the physical position of a species within the ecosystem.
Species were categorised as: 1) benthic, if a species lives on the
seafloor; 2) pelagic, if a species lives close to the surface; 3)
benthopelagic, if it moves between and connects the aforementioned
environments; 4) demersal, if it lives and feeds on, or near, the bottom
of the sea; and 5) land-based, if the consumer is not strictly aquatic
but feeds predominantly on marine species. Species habitat affiliations
were retrieved from \citet{Jacob2011}.

To study the relationship between species mean interaction strength
(weighted property) and the unweighted species properties, we performed
linear regression analyses between the log mean interaction strength and
each of the aforementioned unweighted properties. Thus, we considered
the interaction strength as the dependent variable and the given
unweighted property as the independent variable, and obtained the
coefficients (slope and intercept) for the linear model. Models were
fitted using the least squares approach. We also explored the mean
interaction strength distribution with the species habitat.

@@

To analyse the impact of species on food web stability, we performed
extinction simulations deleting one species at a time, that is for every
extinction, network size was reduced by one species only. After each
extinction, we calculated the stability of the network minus the removed
species (489 nodes) and compared it with that of the whole network (490
nodes in total). To calculate stability, we used the mean of the real
part of the maximum eigenvalue of the Jacobian matrix using randomized
Jacobians, keeping the predator-prey sign structure fixed
\citep{Allesina2008, Grilli2016}. This stability index indicates a more
stable food web when it is negative. We performed 1000 simulations for
each species removal and obtained a mean maximum eigenvalue for each
case. Finally, we statistically analysed this difference with an
Anderson-Darling test considering a p-value \textless{} 0.01
\citep{Scholz1987}. If the difference between the networks without and
with the removed species is positive, then the stability of the whole
food web is higher without the targeted species, in other words this
species makes the network less stable. If the difference is negative,
then the stability of the whole food web is lower without the targeted
species, i.e., this species ahs a stabilizing effect. A detailed
description on the stability calculations can be found in the
supplementary material.

To identify the species with the highest effect on food web stability,
we plotted the results of each species' extinction and its effect on
food web stability, considering weighted (interaction strength) and
unweighted properties, and species habitat.

@@

Our analyses show that the distribution of species interaction strength
(IS) at the network level is asymmetric, i.e., the Weddell Sea food web
contains many weak interactions and only a few strong ones. This finding
is consistent with many previous theoretical and empirical studies
\citep[e.g.][]{McCann1998, Neutel2002, Emmerson2004, Wootton2005, Kortsch2021}.
The asymmetric distribution of IS in food webs has been interpreted as
an explanation for the persistence of complex communities in nature
\citep{Bascompte2005, Allesina2015, Nilsson2016}. Here we show that this
pattern is also prevalent in the Weddell Sea, one of the most complex
food webs to date, comprising 490 species and 16041 predator-prey
interactions. This finding is in someway validating the method we used,
validation of allometric methods of IS estimation not including
interaction dimensionality has been performed for microcosmos of
relatively few species \citep{Jonsson2018}.

@@

We employed a range of descriptors using both unweighted and weighted
food web properties to characterise the dynamic and multifaceted nature
of the Weddell Sea food web. Our results show a positive relationship
between IS and trophic level, and between IS and species degree. In the
Weddell Sea, species with high degree also tend to have high mean ISs.
This positive relationship between IS and species degree reinforces the
central role of species with many interactions: species with a high
degree (hubs) have a large impact on overall food web structure and
functioning \citep{Dunne2002a, Kortsch2015}. On the other hand, the
positive IS-trophic level relationship contradicts studies that suggest
that mid-trophic level species (e.g.~krill, mesopelagic fish, squid) are
involved in the major pathways of energy flow in high-latitude marine
ecosystems
\citep{Pinkerton2014, Murphy2016, McCormack2020, Riccialdelli2020}. Such
contradiction could be explained by the lack of species biomass
information in the calculation of IS we applied here \citep{Pawar2012}.
Although this methodology allows information on species biomass or
density to be included, this type of data was not available for the
majority of species of the Weddell Sea food web.

Overall, the combination of information on the quantity and quality of
interactions and its relationship enables a robust assessment of the
species' role in the stability of the food web \citep{Cirtwill2018a}.

@@

Only a few species play a key role with respect to the Weddell Sea food
web stability, according to the stability index employed in this study.
This is in concordance with other studies on complex empirical food webs
in marine ecosystems in the Arctic and other locations in Antarctica
\citep{Kortsch2015, Marina2018, Rodriguez2022}. These key species are
characterised by a particular set of food web properties: high to mean
IS; mid to high trophic level; a relatively high number of interactions;
and mid to low trophic similarity. In a previous study on sequential
extinction simulations for the Weddell Sea food web \citep{Jacob2011},
it was found that larger bodied-sized species could be lost without
causing a collapse of the network. A major caveat of this finding, also
recognised by the authors, was that population dynamics were ignored and
hence no top-down extinctions, or other indirect effects, could occur.
In our study we considered such top-down effects by including
information on the species IS, which is of paramount importance when
analysing the response of perturbations in ecological communities
\citep{McCann1998, Montoya2009, Novak2011}. Thus, our study suggests
that species with high mean IS and high trophic levels need to be
considered with particular attention when trying to predict the effects
of perturbations on the Weddell Sea ecosystem. This conclusion is
further reinforced by the finding that these species have mid to low
trophic similarity, which means that few other species of the food web
can occupy the same trophic role. In a review, it was emphasised that
polar pelagic communities are particularly sensitive to changes due to a
low functional redundancy at key trophic levels \citep{Murphy2016}. Here
we provide a broader analysis of the species impact on food web
robustness by including species from all habitats (benthic, pelagic and
land-based). This suggests that the sensitivity of marine polar
ecosystems to environmental perturbations is a concern also beyond the
pelagic realm.

@@

Our study goes beyond the current understanding of how species influence
ecosystem structure and stability in the Weddell Sea in particular, and
in most polar regions in general \citep{Murphy2016, McCormack2021}. In
the same analysis we integrated information on weighted (IS) and
unweighted species properties, enabling a more complete assessment of
the species' role realted food web structure and stability, and allowing
us to identify species and their characteristics which can have a
destabilising or stabilising effect on the food web.

We consider that the information provided in this study is important for
the development of effective policies and management strategies,
particularly given the ongoing initiative to implement a Marine
Protected Area (MPA) in the Weddell Sea region \citep{Teschke2021}.

@@

\begin{figure}
\includegraphics[width=12cm]{Fig.2_ToyFoodWeb} \caption{Scheme of a network showing the weighted and unweighted properties we used to characterize the species of the Weddell Sea food web. Directed arrows indicate the flow of energy; the width of the arrow represents the interaction strength of it.}\label{fig:unnamed-chunk-2}
\end{figure}
